Automating Verification of MPC Security

### 2023-06-17 popl24/composition.tex
checkpoint

In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality in Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates} includes the following:
\begin{itemize}
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,gate:6tt2]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled  table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol.
\item \ttt{encode}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
\begin{example}
  \label{example-andcircuit}
The following program uses our YGC library to define
a ciruit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
\begin{verbatimtab}
  andgate(0,s1,s2);
  garbledecode(0);
  let secrets = encode(s1,s2) in
  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
\end{verbatimtab}
\end{example}
We have verified passive security of the $\fedprot$ protocol
generated by this and other small circuits using the
technique described in Lemma \ref{lemma-bruteforce-nimo}.
But obviously large circuits with thousands of gates would be
intractable to verify with this method. In the next Section
we discuss compositional methods to address this issue.

\subsection{YGC Gate Pre-~and Post-Conditions}

A basic intuition about how garbled gates work is that they are
``nearly'' passive secure, modulo the feature that outputs of
individual logic gates in circuits are encryped. That is, each gate
enjoys $\NIMO$, except the output is not in the clear, but correlated
with the flips that the garbler sampled for the gate's output wire
label, both key and pointer bits. We call this \emph{Garbled $\NIMO$},
or $\gNIMO$. To clarify this definition, recall that Definition \ref{def-progd}
posits a variable $\itv$ to refer to the expression $\be$ when
considering the distribution $\progd(\prog,\be)$.
\begin{definition}[Garbled $\NIMO$]
  We write $\gNIMO(\prog,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} =
  \be_{\ttt{p}}\}, g)$ with $\iov(\prog) = S \cup V$ iff for all $H$,
  $C$ with $|C| \le |H|$, for all $\store \in \mems(S_C \cup V_C)$,
  for both $w \in \{\ttt{p},\ttt{k}\}$, and for all $\stores$ with
  domain $X = S_C \cup V_C \cup \{ \itv, \flip{2}{\ttt{gate:}g.w} \}$
  such that:
  $$
  \stores = \{ \store' \mid \store \subset \store' \wedge 
  \store'(\itv) = \store'(\flip{2}{\ttt{gate:}g.w}) \} 
  $$
  or
  $$
  \stores = \{ \store' \mid \store \subset \store' \wedge 
  \store'(\itv) = \neg\store'(\flip{2}{\ttt{gate:}g.w}) \} 
  $$
  %where for any $\beta$:
  %$$\store^2 = \store\{ \flip{2}{\ttt{gate:}g.w} \mapsto \beta \}\{ \itv \mapsto \beta \}$$
  %or
  %$$
  %\store^2 = \store\{ \flip{2}{\ttt{gate:}g.w} \mapsto \beta \}\{ \itv \mapsto \neg\beta \}
  %$$
  we have:
  $$
  \margd{(\condd{\progd(\prog,\be_w)}{\stores_{X-{V_C}}})}{S_H} =
  \margd{(\condd{\progd(\prog,\be_w)}{\stores})}{S_H}
  $$
\end{definition}

\begin{lemma}
  \label{lemma-scope}
  If $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) *
  (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$ and
  $\flips(\prog_1) \cap \flips(\prog_2) = \varnothing$ then
  $(\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_1)}) *
  (\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_2)})$ for any
  $\prog_1'$ where $\prog_1';\prog_2$ is safe and $\flips(\prog_1')
  \cap \flips(\prog_2) = \varnothing$.
\end{lemma}

\begin{definition}
  We write $g \in \prog$ iff $\view{1}{\ttt{gate:}g\ttt{tt}i} \in \iov(\prog)$
  and $\view{1}{\ttt{gate:}g\ttt{pt}i} \in \iov(\prog)$ for all $0 < i \le 4$,
  or  $\view{1}{\ttt{gate:}gi\ttt{.k}} \in \iov(\prog)$
  and $\view{1}{\ttt{gate:}gi\ttt{.p}} \in \iov(\prog)$ for all $0 < i \le 2$.
\end{definition}

\begin{lemma}
  \label{lemma-gnimo}
  If $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
  and $\flips(\prog_1) \cap \flips(\prog_2) = \varnothing$ and
  $\gNIMO(\prog_1;\prog_2,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$ for
  $g \in \prog_1$,
  then $\gNIMO(\prog_1';\prog_2,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$
  for any $\prog_1'$ where $\prog_1';\prog_2$ is safe and
  $\flips(\prog_1') \cap \flips(\prog_2) = \varnothing$.
\end{lemma}

\begin{lemma}[Input Encoding]
  Given well-typed $\prog_1;E[\ttt{encode}(s_1,s_2)]$ where:
  $$
  \config{\prog_1}{E[\ttt{encode}(s_1,s_2)]} \redxs
  \config{\prog_1;\prog_2}{E[\ttt{\{ wv1 =} v_1\ttt{; wv2 = } v_2 \ttt{\}}]}
  $$
  Then:
  $$\gNIMO(\prog_1;\prog_2,v_1,s_1) \wedge \gNIMO(\prog_1;\prog_2,v_2,s_2)$$
\end{lemma}

Our aim now is to express that $\gNIMO$ is an invariant preserved throughout
the circuit by demonstrating pre-~and post-conditions for component execution.
Our formulation will assume a protocol definition where the garbler and
evaluator coordinate garbling, sharing, and evaluation of gates iteratively,
although the generated $\fedprot$ program could be rewritten so the garbler
shares the entire circuit before execution by the evaluator. As a sanity
condition we will assume all $\metaprot$ programs we consider in this
section are well-typed.

First, we show that encoding of input secrets for use by the evaluator
establishes the $\gNIMO$ invariant.

\begin{verbatimtab}
andgg(g, wla, wlb, wlc, wva, wvb) {
andgate(g, wla, wlb, wlc);
evalgate(g, wva, wvb)
}
\end{verbatimtab}

\begin{definition}
  We write $\owl(\prog, \{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$
 iff for all $b$ and both $w \in \{\ttt{p},\ttt{k}\}$:
  $$
  (\margd{(\condd{\progd(\prog,\be_{w})}{\{ \flip{2}{g.w} \mapsto b \}})}{\itv})(\{ \itv \mapsto b\}) = 1
  $$
\end{definition}

\begin{lemma}[Input Encoding]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{encode}(w,v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
$$
If there exists gate identifiers $g_1, g_2$ such that:
\begin{enumerate}
  \item $g_1 \ne g_2 \wedge g_1,g_2 \not\in \gates(\prog_1)$
  \item $\owl(\prog_1,v_1,g_1) \wedge \owl(\prog_1,v_2,g_2)$
\end{enumerate}
then:
\begin{enumerate}
\item $g_1,g_2 \in  \gates(\prog_2)$
\item $\gNIMO(\prog_1;\prog_2,v.\ttt{wv1},g_1) \wedge \gNIMO(\prog_1;\prog_2,v.\ttt{wv2},g_2)$
\item $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
\end{enumerate}
\end{lemma}

\begin{lemma}[Composition ($\eand$)]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{andgg}(g,v_1,\ldots,v_5)]} \redxs \config{\prog_1;\prog_2}{E[v_6]}
$$
If there exist gate identifiers $g_1, g_2$ such that:
\begin{enumerate}
  \item $g_1 \ne g_2 \ne g \wedge g_1,g_2 \in \gates(\prog_1) \wedge g \not\in \gates(\prog_1)$
  \item $\owl(\prog_1,v_1,g_1) \wedge \owl(\prog_1,v_2,g_2)$
  \item $\gNIMO(\prog_1,v_4,g_1) \wedge \gNIMO(\prog_1,v_5,g_2)$
\end{enumerate}
then:
\begin{enumerate}
  \item $g \in \gates(\prog_2) \wedge \owl(\prog_1;\prog_2,v_3,g)$
  \item $\gNIMO(\prog_1;\prog_2,v_6,g)$
  \item $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
\end{enumerate}
\end{lemma}

\begin{lemma}[Decoding]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{decoder}(v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[\be]}
$$
If there exists gate identifier $g \in \gates(\prog_1)$ such that:
\begin{enumerate}
  \item $\owl(\prog_1,v_1,g)$
  \item $\gNIMO(\prog_1,v_2,g)$
\end{enumerate}
Then $\NIMO(\prog_1;\prog_2;\eassign{x}{\be})$.
\end{lemma}

>>>>

In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality in Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates} includes the following:
\begin{itemize}
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,gate:6tt2]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled  table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol.
\item \ttt{encode}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
\begin{example}
  \label{example-andcircuit}
The following program uses our YGC library to define
a ciruit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
\begin{verbatimtab}
  andgate(0,s1,s2);
  garbledecode(0);
  let secrets = encode(s1,s2) in
  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
\end{verbatimtab}
\end{example}
We have verified passive security of the $\fedprot$ protocol
generated by this and other small circuits using the
technique described in Lemma \ref{lemma-bruteforce-nimo}.
But large circuits with thousands of gates would be
intractable to verify with this method. In the next Section
we discuss compositional methods to address this issue.

\subsection{Verification of Pre-~and Post-Conditions}

A basic intuition about YGC is that garbled gates considered
individually are ``nearly'' passive secure, modulo the feature that
outputs of individual logic gates in circuits are encryped. That is,
each gate enjoys an encrypted variant of$\NIMO$ such that the relevant
output is not in the clear but correlated flips sampled for the gate's
output wire label by the garbler, both key and pointer bits. We call
this \emph{Garbled $\NIMO$}, or $\gNIMO$. In the definition of
$\gNIMO$ we consider whether a given value $\itv$ correlates
positively or negatively to the flip chosen for a wire lable, which
can be either $1$ or $0$ uniformly- recall that
Definition \ref{def-progd} posits a variable $\itv$ to refer to the
expression $\be$ when considering the distribution
$\progd(\prog,\be)$.
\begin{definition}[Garbled $\NIMO$]
  We write $\gNIMO(\prog,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} =
  \be_{\ttt{p}}\}, g)$ with $\iov(\prog) = S \cup V$ iff for all $H$,
  $C$ with $|C| \le |H|$, for all $\store \in \mems(S_C \cup V_C)$,
  for both $w \in \{\ttt{p},\ttt{k}\}$, and for all $\stores$ with
  domain $X = S_C \cup V_C \cup \{ \itv, \flip{2}{\ttt{gate:}g.w} \}$
  such that:
  $$
  \stores = \{ \store' \mid \store \subset \store' \wedge 
  \store'(\itv) = \store'(\flip{2}{\ttt{gate:}g.w}) \} 
  $$
  or
  $$
  \stores = \{ \store' \mid \store \subset \store' \wedge 
  \store'(\itv) = \neg\store'(\flip{2}{\ttt{gate:}g.w}) \} 
  $$
  %where for any $\beta$:
  %$$\store^2 = \store\{ \flip{2}{\ttt{gate:}g.w} \mapsto \beta \}\{ \itv \mapsto \beta \}$$
  %or
  %$$
  %\store^2 = \store\{ \flip{2}{\ttt{gate:}g.w} \mapsto \beta \}\{ \itv \mapsto \neg\beta \}
  %$$
  we have:
  $$
  \margd{(\condd{\progd(\prog,\be_w)}{\stores_{X-{V_C}}})}{S_H} =
  \margd{(\condd{\progd(\prog,\be_w)}{\stores})}{S_H}
  $$
\end{definition}

\subsubsection{Verification Witnesses}

Our aim is to demonstrated that $\gNIMO$ is preserved by gates within circuits,
where preservation is expressed via pre-~and post-conditions. We can use
techniques in Section \ref{section-bruteforce} to automatically verify postconditions
for components, using witness programs that satisfy preconditions prior to
component execution. For example, we can automatically verify that $\ttt{encode}$
generates a program and wire values the enjoy $\gNIMO$. Then, to verify
that we can verify
that the $\minifed$ program and wire value generated by the following program satisfies
$\gNIMO$:
\begin{verbatimtab}
  let secrets = encode(s1,s2) in
  andgate(0,s1,s2); evalgate(secrets.wv1,secrets.wv2)
\end{verbatimtab}
However, we need to establish that $\ttt{encode(s1,s2)}$ is an
adequate witness to correctness, so our automated verification generalizes to
arbitrary circuit contexts.

An important part of this argument is probabilistic independence,
and in related reasoning we can leverage prior work on probabilistic
separation logic \cite{barthe2019probabilistic}. We will use an
analog of their separation formula, which we define in our setting as follows:
\begin{definition}
  We write $(\margd{\pdf{X}}{Y}) * (\margd{\pdf{X}}{X-Y})$ iff
  $\pdf{X}(\store) = \pdf{X}(\store_{Y}) * \pdf{X}(\store_{X-Y})$
  for all $\store \in \mems(X)$.
\end{definition}

We aim to show that gates are probabilistically independent of
each other (i.e., are separated), and this independence supports
correctness-preserving composition. Noting that gates have
naming conventions, and that gates are distinguished by gate
identifiers $g$, we can define what we mean by a gate
$g$ being in a given program $\prog$, written $g \in \prog$. 
\begin{definition}
  We write $g \in \prog$ iff $\view{1}{\ttt{gate:}g\ttt{tt}i} \in \iov(\prog)$
  and $\view{1}{\ttt{gate:}g\ttt{pt}i} \in \iov(\prog)$ for all $0 < i \le 4$,
  or  $\view{1}{\ttt{gate:}gi\ttt{.k}} \in \iov(\prog)$
  and $\view{1}{\ttt{gate:}gi\ttt{.p}} \in \iov(\prog)$ for all $0 < i \le 2$.
\end{definition}

A critical property is that separation is preserved by safe
(in the sense of Theorem \ref{theorem-metalang-safety}) substitution
of programs, assuming disjointness of flips used in programs separated
programs. 
\begin{lemma}
  \label{lemma-scope}
  If $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) *
  (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$ and
  $\flips(\prog_1) \cap \flips(\prog_2) = \varnothing$ then
  $(\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_1)}) *
  (\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_2)})$ for any
  $\prog_1'$ where $\prog_1';\prog_2$ is safe and $\flips(\prog_1')
  \cap \flips(\prog_2) = \varnothing$.
\end{lemma}
\begin{proof}
  \cnote{The Lemma statement may be slightly off, there may be more restrictions on $\prog_1$.
  But generally this result follows by results from \cite{barthe2019probabilistic.}}
\end{proof}

Another important property is that $\gNIMO$ is preserved by substitution
for a witness program. This follows by Lemma \ref{lemma-scope} and definition
of $\gNIMO$. 
\begin{lemma}
  \label{lemma-gnimo}
  If $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
  and $\flips(\prog_1) \cap \flips(\prog_2) = \varnothing$ and
  $\gNIMO(\prog_1;\prog_2,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$ for
  $g \in \prog_1$,
  then $\gNIMO(\prog_1';\prog_2,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$
  for any $\prog_1'$ where $\prog_1';\prog_2$ is safe and
  $\flips(\prog_1') \cap \flips(\prog_2) = \varnothing$.
\end{lemma}

\subsubsection{Pre-~ and Post-Conditions}
\label{section-pre-post}
Now we can establish relevant pre-~and post-conditions for the
top-level YGC functions defined in Figure \ref{fig-ygc-gates}. We note
that in addition to the automated verification mechanisms described in
Section \ref{section-bruteforce}, type safety in $\metaprot$ plays an
important role, in part by ensuring that gates are uniquely defined
(as views).

Our strategy is to consider input encoding, internal gates, and
output decoding separately. To begin, we show that input encoding
establishes generates a program and wire values that initialize
the $\gNIMO$ invariant in the circuit. There is no precondition
witness needed for this result, which holds in any type-safe
program context since the variables used by $\ttt{encode}$
are all fresh. 
\begin{lemma}[Input Encoding]
  \label{lemma-encode}
  Given well-typed $\prog_1;E[\ttt{encode}(s_1,s_2)]$ where:
  $$
  \config{\prog_1}{E[\ttt{encode}(s_1,s_2)]} \redxs
  \config{\prog_1;\prog_2}{E[\ttt{\{wv1=}v_1\ttt{;wv2=}v_2\ttt{\}}]}
  $$
  Then:
  $$\gNIMO(\prog_1;\prog_2,v_1,s_1) \wedge \gNIMO(\prog_1;\prog_2,v_2,s_2)$$
\end{lemma}

\begin{proof}
  We have automatically verified
  $\gNIMO(\prog_2,v_1,\ttt{s1})$ and $\gNIMO(\prog_2,v_1,\ttt{s1})$
  where:
  $$
  \config{\varnothing}{\ttt{encode(s1,s2)}} \redxs
  \config{\prog_2}{\ttt{\{wv1=}v_1\ttt{;wv2=}v_2\ttt{\}}}
  $$
  using the method described in Section \ref{section-bruteforce-tables}.
  Given arbitrary $\prog_1$ such that $\prog_1;\ttt{encode}(s_1,s_2)$
  is well-typed, hence $\prog_1;\prog_2$ is safe, 
  since $\ttt{encode}$ uses unique secrets and flips per gates and
  gates (views) are not redefined in safe programs,
  $(\iov(\prog_1) \cup \flips(\prog_1)) \cap (\iov(\prog_2) \cup
  \flips(\prog_2)) = \varnothing$. This implies 
  $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) *
  (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$, so the result follows
  by Lemma \ref{lemma-gnimo}.
\end{proof}

One nuance in our results for internal gates and for decoding is that the relevant
compositional units are the complete related subprotocols, including both
the garbler's construction of the gates and the evaluator's evaluation of
them. We therefore make the following definitions. However, we note that
our formal results are applicable to the YGC style where the garbler shares
the entire circuit prior to evaluation, rather than gate-by-gate during
evaluation. 
\begin{definition}
  \label{ygc-modules}
  We define a composable internal \ttt{and} gate sharing and evaluation function
  called $\ttt{andgg}$, and an output decoder gate share and evaluation function called
  $\ttt{decode}$, as follows. 
\begin{verbatimtab}
  andgg(g, ga, gb, wva, wvb) { andgate(g, ga, gb); evalgate(g, wva, wvb) }

  decode(g, v) { garbledecode(g); evaldecode(v) }
\end{verbatimtab}
\end{definition}

Now we can demonstrate that our $\ttt{and}$ gate definition preserves
$\gNIMO$, and additionally that internale gates are probabilistically independent.
This latter fact is crucial to compositionality, and allows us for automatically
verify the circuit in isolation, with input encoding serving as an adequate input
witness for generalization. 
\begin{lemma}[Composition ($\eand$)]
  \label{lemma-compose}
Given well-typed $\prog_1;E[\ttt{andgg}(g,g_1,g_2,v_1,v_2)]$ where:
$$
\config{\prog_1}{E[\ttt{andgg}(g,g_1,g_2,v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
$$
If the following preconditions hold:
\begin{enumerate}
\item $g_1 \ne g_2$
\item $\gNIMO(\prog_1,v_1,g_1) \wedge \gNIMO(\prog_1,v_2,g_2)$ 
\end{enumerate}
then we have as postconditions:
\begin{enumerate}
  \item $\gNIMO(\prog_1;\prog_2,v,g)$
  \item $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
\end{enumerate}
\end{lemma}
\begin{proof}
  We have automatically verified the postconditions (1) and (2) for the particular
  program $\prog_1;\prog_2$ resulting from execution of:
  $$e\quad \defeq\quad \ttt{let gs = encode(s1,s2) in andgg(0,s1,s2,gs.wv1,gs.wv2)}$$
  where:
  $$
  \config{\varnothing}{e} \redxs
  \config{\prog_1}{\ttt{andgg}(\ttt{0},\ttt{s1},\ttt{s2},v_1,v_2)} \redxs \config{\prog_1;\prog_2}{v}
  $$
  By Lemma \ref{lemma-encode} we have that
  $\gNIMO(\prog_1,v_1,\ttt{s1}) \wedge \gNIMO(\prog_1,v_2,\ttt{s2})$. 
  And since $\ttt{andgate}$ generates unique flips per gate, and well-typedness ensures
  uniqueness of gates, we can generalize the result to replace $\prog_1$ with arbitrary $\prog_1'$
  such that $\prog_1';\prog_2$ is safe,
  applying Lemma \ref{lemma-scope} to obtain postcondition (2) and Lemma \ref{lemma-gnimo}
  to obtain postcondition (1). 
\end{proof}
Finally, we can demonstrate that decoding correctly casts a garbled output into the
clear, and thus establishes $\NIMO$ for the garbled circuit that precedes it.
\begin{lemma}[Decoding]
  \label{lemma-decode}
Given well-typed $\prog_1;E[\ttt{decode}(g,v)]$ where
$$
\config{\prog_1}{E[\ttt{decode}(g,v)]} \redxs \config{\prog_1;\prog_2}{E[\be]}
$$
If $\gNIMO(\prog_1,v,g)$, then $\NIMO(\prog_1;\prog_2;\eassign{\outv}{\be})$.
\end{lemma}
\begin{proof}
  We have automatically verified $
  \progd(\prog,\be)(\{ \itv \mapsto 1 \}) = 1$ where:
  $$\config{\varnothing}{\ttt{decode(g,\{ k = flip[2, gate:g.k]; p = flip[2,gate:g.p] \})}}
    \redxs \config{\prog}{\be}$$
    and also $
  \progd(\prog,\be)(\{ \itv \mapsto 0 \}) = 1$ where:
  $$\config{\varnothing}{\ttt{decode(g,\{ k = not flip[2, gate:g.k]; p = not flip[2,gate:g.p] \})}}
    \redxs \config{\prog}{\be}$$
  The result follows by definition of $\gNIMO$ and $\NIMO$.
\end{proof}
